### 2020-04-15 serial.tex
more

>>>>

Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
We provide a theoretical basis for understanding serial intervals and show that both generation and serial intervals provide a correct link between $r$ and $\mathcal R$.
Our analysis further reveals gap in current understanding and practical approaches to studying serial intervals.

First, we demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
Previous studies have shown that generation interval can be either measured forward or backward;
we generalize their ideas and show that these ideas can be applied to all distributions.
Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.
Several epidemic analyses have attempted to reconstruct symptom onset or infection dates for each case from the confirmed dates while assuming a constant delay distribution;
these assumptions translate to assuming a constant backward delay distribution.
Although such assumption may be able to approximately match the time scale of an epidemic, 
our analysis reveals that it is not a safe assumption.

Using cohort-based approaches, we can define forward and backward serial intervals.
The forward serial-interval distribution describes the
